An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-05-24 EconGrowth.Rnw
More changes related to f_enduse/intake moving to f_intake/wholesale.

To calculate the exergy of animal and human muscle power, the food-to-work conversion efficiency ($\eta_{food \rightarrow work}$) and the ratio of food enduse to food intake ($f_{enduse/intake}$) were included.

@@

\begin{equation} \label{eq:human_muscle_exergy}
  X_{workers} = \eta_{food \rightarrow work,workers} f_{enduse/intake} Q_{workers}
\end{equation}

@@

\begin{table} \caption{Food intake-to-wholesale ratios ($f_{intake/wholesale}$) for all countries.} \label{tab:f_intake_wholesale}
  \begin{center}
    \begin{tabular}{r c c c c c c c c c}
      Country & US & UK & JP & CN & ZA & SA & IR & TZ & ZM \\
      \hline
      $f_{enduse/intake}$ & 0.62 & 0.65 & 0.76 & 0.76 & 0.87 & 0.72 & 0.72 & 0.72 & 0.72\\
    \end{tabular}
  \end{center}
\end{table}

>>>>

To calculate the exergy of animal and human muscle power, the food-to-work conversion efficiency ($\eta_{food \rightarrow work}$) and the ratio of food intake to food available at wholesale ($f_{intake/wholesale}$) were included.

@@

\begin{equation} \label{eq:human_muscle_exergy}
  X_{workers} = \eta_{food \rightarrow work,workers} f_{intake/wholesale} Q_{workers}
\end{equation}

@@

\begin{table} \caption{Food intake-to-wholesale ratios ($f_{intake/wholesale}$) for all countries.} \label{tab:f_intake_wholesale}
  \begin{center}
    \begin{tabular}{r c c c c c c c c c}
      Country & US & UK & JP & CN & ZA & SA & IR & TZ & ZM \\
      \hline
      $f_{intake/wholesale}$ & 0.62 & 0.65 & 0.76 & 0.76 & 0.87 & 0.72 & 0.72 & 0.72 & 0.72\\
    \end{tabular}
  \end{center}
\end{table}
